### 2018-01-23 source/intro/RIME.tex
changed architecture, added skeleton of main chapters

\section{The RIME Formalism}
\label{section.RIME}
\pg
While radio interferometry has historically been a complex business (\citepads{2001isra.book.....T}), modern radio interferometry is based on the Radio Interferometer's Measurement Equation, a powerful and elegant formalism which underpins modern calibration and imaging algorithms. In this section, I will give a simplified account of this formalism as described in \citepads{2011A&A...527A.106S} and its companion papers\footnote{\citepads{2011A&A...527A.107S}, \citepads{2011A&A...527A.108S} and \citepads{2011A&A...531A.159S}}. This will form the theoretical basis on which further sections will expand. I cannot overstate the importance of the RIME as the foundation of modern calibration and imaging algorithms.

@@

\subsection{Setting up the RIME: a single point source}
\label{section.RIME.setup}

@@

\subsection{Expanding our Jones Chain}
\label{section.RIME.JonesChain}
\pg
Having written our RIME as a matrix multiplication problem, we can now begin to differentiate between different types of Jones matrices. $\Jones_p$ describes the \emph{aggregate} effects which occur over the course of the signal's propagation to our antenna $p$. It can be split into a Jones chain of $n$ separate matrices, corresponding to different effects:
\begin{align}
\displaystyle \Jones_{sp}^H &= \prod_1^n \Jones_{nsp}^H = \Jones_{1sp}^H \Jones_{2sp}^H ... \Jones_{nsp}^H\\
\displaystyle \Jones_{sp}   &= \Jones_{nsp}...\Jones_{2sp} \Jones_{1sp}
\end{align}

@@

\subsubsection{Geometric Effects: the Phase Delay Jones Matrix}
\label{section.RIME.JonesChain.Kjones}

@@

\subsubsection{The Coherency Matrix}
\label{section.RIME.JonesChain.CoherencyMatrix}

@@

\subsection{Multiple Point Sources}
\label{section.RIME.MultiplePointSources}

@@

\subsection{Diffuse Emission: the Full-sky RIME}
\label{section.RIME.FullSky}

\subsubsection{Deriving the Fully-Sky RIME}
\label{section.RIME.FullSky.derivation}
\pg
If we want to be able to take diffuse emission properly into account, we must go from our set of discrete point sources $\Bmatrix_s$ and integrate the underlying continuous brightness distribution $\Bmatrix(\direction)$ over all possible directions. This gives us the following expression:
\begin{equation}
\Vis_{pq} = \int_{4\pi} \Jones_p(\direction) \Bmatrix(\direction) \Jones_q^H(\direction)d\Omega
\end{equation}

@@

\subsubsection{Recovering the van Cittert-Zernike Theorem}
\label{section.RIME.FullSky.CVZ}

@@

\subsection{Time-dependent Jones matrices, Smearing, and Decoherence}
\label{section.RIME.TimeDep}

\subsubsection{Time-dependence of Jones matrices}
\label{section.RIME.TimeDep.Jones}

@@

\subsubsection{Smearing and Decoherence}
\label{section.RIME.TimeDep.Decoherence}

@@

\subsection{Noise}
\label{section.RIME.noise}

>>>>

\chapter{The RIME Formalism}
\label{section.RIME}
\pg
While radio interferometry has historically been a complex business (\citepads{2001isra.book.....T}), modern radio interferometry is based on the Radio Interferometer's Measurement Equation, a powerful and elegant formalism which underpins modern calibration and imaging algorithms. In this section, I will give a simplified account of this formalism as described in \citepads{2011A&A...527A.106S} and its companion papers\footnote{\citepads{2011A&A...527A.107S}, \citepads{2011A&A...527A.108S} and \citepads{2011A&A...531A.159S}}. This will form the theoretical basis on which further sections will expand. I cannot overstate the importance of the RIME as the foundation of modern calibration and imaging algorithms.

@@

\section{Setting up the RIME: a single point source}
\label{section.RIME.setup}

@@

\section{Expanding our Jones Chain}
\label{section.RIME.JonesChain}
\pg
Having written our RIME as a matrix multiplication problem, we can now begin to differentiate between different types of Jones matrices. $\Jones_p$ describes the \emph{aggregate} effects which occur over the course of the signal's propagation to our antenna $p$. It can be split into a Jones chain of $n$ separate matrices, corresponding to different effects:
\begin{align}
\displaystyle \Jones_{sp}^H &= \prod_1^n \Jones_{nsp}^H = \Jones_{1sp}^H \Jones_{2sp}^H ... \Jones_{nsp}^H\\
\displaystyle \Jones_{sp}   &= \Jones_{nsp}...\Jones_{2sp} \Jones_{1sp}
\end{align}

@@

\subsection{Geometric Effects: the Phase Delay Jones Matrix}
\label{section.RIME.JonesChain.Kjones}

@@

\subsection{The Coherency Matrix}
\label{section.RIME.JonesChain.CoherencyMatrix}

@@

\section{Multiple Point Sources}
\label{section.RIME.MultiplePointSources}

@@

\section{Diffuse Emission: the Full-sky RIME}
\label{section.RIME.FullSky}

\subsection{Deriving the Fully-Sky RIME}
\label{section.RIME.FullSky.derivation}
\pg
If we want to be able to take diffuse emission properly into account, we must go from our set of discrete point sources $\Bmatrix_s$ and integrate the underlying continuous brightness distribution $\Bmatrix(\direction)$ over all possible directions. This gives us the following expression:
\begin{equation}
\Vis_{pq} = \int_{4\pi} \Jones_p(\direction) \Bmatrix(\direction) \Jones_q^H(\direction)d\Omega
\end{equation}

@@

\subsection{Recovering the van Cittert-Zernike Theorem}
\label{section.RIME.FullSky.CVZ}

@@

\section{Time-dependent Jones matrices, Smearing, and Decoherence}
\label{section.RIME.TimeDep}

\subsection{Time-dependence of Jones matrices}
\label{section.RIME.TimeDep.Jones}

@@

\subsection{Smearing and Decoherence}
\label{section.RIME.TimeDep.Decoherence}

@@

\section{Noise}
\label{section.RIME.noise}

### 2018-01-23 source/intro/calibration.tex
changed architecture, added skeleton of main chapters

\section{Calibration Methods in Radio Interferometry}\label{section.calibration}
\pg
In this section, we will discuss the implementation of interferometric array calibration. Our analysis will be based on the RIME formalism described in \cref{section.RIME}. One key metric of calibration quality is the \emph{dynamic range} (DR). High dynamic ranges mean that a high contrast has been obtained, and fainter sources can be reached. Dynamic range is defined as the following:
\begin{equation}\label{eq.DR}
DR = \frac{flux_{max}}{\max(\sigma_{thermal},\sigma_{artefacts})}
\end{equation}
where $flux_{max}$ is the flux of the brightest source, $\sigma_{thermal}$ the thermal noise in the image, and $\sigma_{artefacts}$ the noise associated with calibration artefacts.

@@

\subsection{First-Generation: Open-Loop Calibration}\label{section.calibration.1gc}

@@

\subsection{Second-Generation: Self-Calibration}\label{section.calibration.2gc}

@@

\subsection{Third-Generation: Direction-Dependent Effects}

>>>>

\section{Calibration Methods in Radio Interferometry}\label{section.calibration}
\pg
In this section, we will discuss the implementation of interferometric array calibration. Our analysis is based on the RIME formalism, described in \cref{section.RIME}. One key metric of calibration quality is the \emph{dynamic range} (DR). High dynamic ranges mean that a high contrast has been obtained, and fainter sources can be reached. Dynamic range is defined as the following:
\begin{equation}\label{eq.DR}
DR = \frac{flux_{max}}{\max(\sigma_{thermal},\sigma_{artefacts})}
\end{equation}
where $flux_{max}$ is the flux of the brightest source, $\sigma_{thermal}$ the thermal noise in the image, and $\sigma_{artefacts}$ the noise associated with calibration artefacts.

@@

\subsection{Generational Analysis}

\subsubsection{First-Generation: Open-Loop Calibration}\label{section.calibration.1gc}

@@

\subsubsection{Second-Generation: Self-Calibration}\label{section.calibration.2gc}

@@

\subsubsection{Third-Generation: Direction-Dependent Effects}
